Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-05-12 doc/manuscript/translocation_pnas_SI.tex
Make three panel model figure and update main text

Multiple genes in our stringent set of outliers have known associations
with amphibian Bd resistance/tolerance. Of particular interest is a
\textasciitilde940kb region on contig 8 that we identified as under
selection, and that contains 8 genes associated with either the MHC
Class I or Class III regions. The order of these genes in the MYL frog
genome is conserved from \emph{Xenopus} \citep{ohta2006} and is
consistent with MHC Class I/III linkage reported in the Komodo dragon
\citep{reed2021}. Numerous studies have linked MHC genes to frog
resistance/tolerance against Bd infection
\citep[e.g.,][]{savage2011, bataille2015}. In addition to the genes in
this region that we describe in the Results section of the main paper,
other genes also deserve mention. For example, we identified the MHC
Class III gene, heat shock protein 70 (HSP70), as occurring in this
region (Figure~\ref{fig-synteny-plot}). Similarly, \citep{byrne2020}
identified an HSP70-binding protein as a candidate gene under selection
in \emph{Atelopus varius} populations recovering after Bd-caused
declines. HSP70 was also highly expressed in Bd-infected versus
uninfected \emph{Xenopus tropicalis} \citep{rosenblum2009}. This MHC
gene cluster lies on the same chromosome as the outlier SNP in RIN3
(Fig. 2 C), a gene associated with
inflammation response that is highly expressed in amputated
\emph{Xenopus} tails \citep{fukazawa2009}.

@@

Second, we performed a local elasticity analysis on \(\lambda\) with
respect to parameters \(\omega\), \(\sigma_{A_R}\), and \(F\) to
determine how small changes in these parameters could influence the
long-run deterministic growth rate of populations.

@@

>>>>

Multiple genes in our stringent set of outliers have known associations
with amphibian Bd resistance/tolerance. Of particular interest is a
\textasciitilde940kb region on contig 8 that we identified as under
selection, and that contains 8 genes associated with either the MHC
Class I or Class III regions. The order of these genes in the MYL frog
genome is conserved from \emph{Xenopus} \citep{ohta2006} and is
consistent with MHC Class I/III linkage reported in the Komodo dragon
\citep{reed2021}. Numerous studies have linked MHC genes to frog
resistance/tolerance against Bd infection
\citep[e.g.,][]{savage2011, bataille2015}. In addition to the genes in
this region that we describe in the Results section of the main paper,
other genes also deserve mention. For example, we identified the MHC
Class III gene, heat shock protein 70 (HSP70), as occurring in this
region (Figure~\ref{fig-synteny-plot}). Similarly, \citep{byrne2020}
identified an HSP70-binding protein as a candidate gene under selection
in \emph{Atelopus varius} populations recovering after Bd-caused
declines. HSP70 was also highly expressed in Bd-infected versus
uninfected \emph{Xenopus tropicalis} \citep{rosenblum2009}. This MHC
gene cluster lies on the same chromosome as the outlier SNP in RIN3
(Fig. 2 C, Fig. 1
A).

@@

Second, we performed a local elasticity analysis on \(\lambda\) with
respect to parameters \(\omega\), \(\sigma_{A_R}\), and \(F\) to
determine how small changes in these parameters could influence the
long-run deterministic growth rate of populations
(Figure~\ref{fig-viability-supp}).

@@

{\centering \includegraphics[width=0.8\textwidth]{figures/pop_viability_figures_for_supp.jpg}

\caption{\label{fig-viability-supp}Sensitivity analysis of the
stage-structured MYL frog model. Elasticity of \(\lambda\) with changes
in 3 parameters: \(\sigma_{A_R}\) (yearly survival probability of
naturally recruited adults), \(\omega\) (yearly probability of
successful recruitment from juveniles to adults), and \emph{F (}number
of eggs produced by a female frog in a year that successfully hatch).
Elasticity is calculated at the default parameter values for each
population and \(\omega\) = 0.3.}
